Additional analysis

### 2019-03-01 02_analysis.Rmd
Use Roboto instead of Encode

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_node(size = 12) +
  geom_dag_edges() +
  geom_dag_text(size = pts(9), family = "Encode Sans Condensed SemiBold") +
  scale_dag() +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

>>>>

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_node(size = 12) +
  geom_dag_edges() +
  geom_dag_text(size = pts(9), family = "Roboto Condensed Bold") +
  scale_dag() +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

### 2019-03-01 03_additional-analysis.Rmd
Wider session info
Use Roboto instead of Encode

txt_gp <- gpar(fontfamily = "Encode Sans Condensed Medium", 
               fontface = "plain", fontsize = 8)

@@

theme_ngos_table <- ttheme_minimal(
  core = 
    list(fg_params = 
           list(hjust = 0, x = 0.1,
                fontsize = 7, fontface = "plain",
                fontfamily = "Encode Sans Condensed Light"),
         bg_params = list(fill = "white")),
  colhead = 
    list(fg_params = 
           list(hjust = 0, x = 0.1, col = "white",
                fontsize = 7, fontface = "plain",
                fontfamily = "Encode Sans Condensed SemiBold"),
         bg_params = list(fill = ngo_cols("blue"))),
  padding = unit(c(4, 2), "mm"))

>>>>

txt_gp <- gpar(fontfamily = "Roboto Condensed", 
               fontface = "plain", fontsize = 8)

@@

theme_ngos_table <- ttheme_minimal(
  core = 
    list(fg_params = 
           list(hjust = 0, x = 0.1,
                fontsize = 7, fontface = "plain",
                fontfamily = "Roboto Condensed Light"),
         bg_params = list(fill = "white")),
  colhead = 
    list(fg_params = 
           list(hjust = 0, x = 0.1, col = "white",
                fontsize = 7, fontface = "plain",
                fontfamily = "Roboto Condensed Bold"),
         bg_params = list(fill = ngo_cols("blue"))),
  padding = unit(c(4, 2), "mm"))
